### 2019-01-29 texs/paper_base.tex
save

\usepackage{listings}
\usepackage{cite}
\usepackage{url}
\usepackage{natbib}
\usepackage[dvipdfmx]{graphicx}

@@

\lstdefinestyle{Csample}{
  language=C,
  tabsize=2,
}

\lstdefinestyle{Asmsample}{
  tabsize=2,
}

\lstset{%
  basicstyle={\small},%
  commentstyle={\small\itshape},%
  keywordstyle={\small\bfseries},%
  % style={myCustomMatlabStyle},
  stringstyle={\small\ttfamily},
  %frame={tb},
  breaklines=true,
  columns=[l]{fullflexible},%
  % numbers=left,%
  xrightmargin=0zw,%
  xleftmargin=3zw,%
  numberstyle={\scriptsize},%
  stepnumber=1,
  numbersep=1zw,%
  lineskip=-0.5ex,%
  captionpos=b
}

\begin{document}
\begin{eabstract}
A decompiler is a tool for recovering a source code from compiled binary data.
There are various decompilers, but they often output a source code that is not intelligible to humans. 
In this thesis, we apply machine translation techniques to generate human intelligible decompiled source codes. 
More specifically, we propose to use recurrent neural networks with attention, 
which have been demonstrated to be useful for machine translation. 
In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
From the experiment, we can observe little improvement in the decompilation result with the use of attention.

\end{eabstract}
\begin{jabstract}
逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
様々な逆コンパイラが存在するが、既存の逆コンパイラはしばしば人間にとって分かりにくいソースコードを出力する。
そこで本論文では、統計的機械翻訳の技術を逆コンパイラに用いた、解析者にとってわかりやすいソースコードを出力する逆コンパイラを提案する。
具体的には、機械翻訳において有用とされる注意機構付き再帰型ニューラルネットワークを用いる。
実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
実験の結果、注意機構を用いることににより、逆コンパイル結果における若干の精度向上が認められた。
\end{jabstract}

@@

These days, the amount of malware has been increasing rapidly.

要参考文献
So the importance of developing malware analysis tools has been rising.
要参考文献
One of these tools is a decompiler, which is a tool for analyzing the behavior of malware. 
This tool generates a C-like pseudocode which represents the behavior of the malware, and analysts can infer the behavior of the malware from the pseudocode.
This is much easier compared to analyzing raw binary codes.

@@

In this thesis, we apply neural networks to the problem of decompilation to generate human-friendly pseudocodes. 
This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks.
They used sequence-to-sequence model, which ignores the structure of the C language code. 
Therefore, we implemented sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code 
結果が向上していれば(and improving the decompilation accuracy.)といいたい。

従来法の何が悪いのかを説明する．たぶんした。
(TODO)このあとに今回やる更に具体的な内容とその成果についてが入る。

TODO(satos)

\section{Related Works}
In this section, we review related works.

\subsection{Decompilation with Machine Learning}

Because perfect decompilation is naturally impossible, there are many machine learning applications for decompilation.

In \cite{Motoneta}, they used the seqence-to-sequence approach, which is a popular technique in the machine translation.

@@

TODO(satos)

@@

\subsection{Improvement of decompilation results}
In this section, we do not try to recover the function name and variable name. 
However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
要参考文献
For example, assume there is a variable X which seems to have a C struct type and has two fields P and Q.
Also, there are two functions F and G which operate with X. 
The function F receives X and another value V, assigns V to the memory indicated by P, adds 8 to P and increases Q. 
The function G receives X, subtracts 8 from P, decreases Q, and returns the value indicated by P.
In the situation, is is estimated that X has a name related to {\sl stuck}, the function F has a name related to {\sl push},
ands G has a name related to {\sl pop}.

@@

\cite{JSNaughty} applied statistical machine translation for this task.

TODO(satos)

変数の性質から統計情報を取り出し、それを元に

They calculated estimated the name of the variable by the functionality of it

\subsection{Neural Network for Program Generation}

@@

A compiler is a program which compiles source code written in language X to other language Y. 
Usually, X is high-level language and Y is relatively low-level language. 
For example, clang compiler translates C language to x64 assembly language, javac compiler translates Java to Java virtual machine code.

A decompiler is a program which aims to reverse the process of a compiler, retrieve a source code of the high-level language X from the source code of the low-level language Y. 
This reversing process is usually insufficient or impossible.
This is because many informaition, such as variable name or function name, are lost when compiling.
Additionally, the program structure described in the high level language are lost too. 
For example, a simple {\sl for statement} can be represented by the combination of a {\sl while statement} and an {\sl if statement}, or the combination of {\sl if statement} and {\sl goto statement}. 
So a decompiler can't distinguish their representation difference, despite in the real situation {\sl for statement} are often used and {\sl goto statement} are rarely.

Existing decompilers are made up with many steps similar to compilers. 
They find patterns in binary data, convert them to more high-level structure, and chain them so that they finally generate high-level psudecode.
Their output psudecodes are sometimes wrong or hard to understand.

% https://github.com/torvalds/linux/blob/70c25259537c073584eb906865307687275b527f/lib/rbtree.c#L528

@@

\begin{figure}
	\begin{tabular}{cc}
		\begin{minipage}[c]{0.5\hsize}
			\lstinputlisting[title={sample C source code},breaklines=false]{bintree.c}
		\end{minipage}
		\\
		\begin{minipage}[c]{0.5\hsize}
			\lstinputlisting[title={result of the Hopper Decompiler}]{hopper.c}
		\end{minipage}
		\begin{minipage}[c]{0.5\hsize}
			\lstinputlisting[title={result of the Snowman Decompiler}]{snowman.c}
		\end{minipage}
	\end{tabular}
	\vspace*{-0.6cm}
	\caption{ decompilation results of existing decompilers for C source code}
	\label{fig:cw}
\end{figure}

Figure~\ref{fig:cw} shows the example decompilation results of the Hopper disassembler and the snowman decompiler 
for a sample C language code.
The Hopper decompiler fails to detect while statements, and the variable {\sl now} is incorrectly analyzed.
The output of snowman seems rather correct, as type {\sl struct tree} is reconstructed to {\sl struct s0}, 
and the {\sl if} statement and {\sl while} statement are correctly restored. 
However, it fails to detect the function epilogue, and the {\sl free} function call is incorrectly analyzed.
Ideally, the decompilers can find correct function ranges and structure of statements, but they failed.

@@

% 189
In this paper, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
The decompilation problem is formulated as follows.

@@

\subsection{Seq-to-Seq}
% This model is called seq2seq (sequence to seqence) model.

@@

@@

Second is the multi-layer reccurent neural networks, introduced in \cite{multi_layer}.

TODO(satos)

@@

\subsection{Sequence-to-Tree}
% 184 words
Compare to natural languages, programming languages obeys rigid grammer, wich is usually context free grammer,  
and it is reasonable to consider the grammer of the programming language in generating programs.
Sequence-to-Tree is a model for generating tree-structured output from sequence input. This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages. 
This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.

@@

The decoder network is a network for generating tree structured output. 
A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
Suppose the tree $ty$ is generated by the action sequence $ [act_1, \dots act_m] $, 
where $ act_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [act_1, \dots act_{k-1}] $. 
Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $, 
so the sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.

@@

They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
However, in our case, we don't need copy the information from the input, because the name information is lost when compiling.
Nevertheless, it is found from the experiments that our decompilers often fail to recover the constant values in the programs.
Therefore, implementing the copying method is left for future work.

@@

\section{Data Collection}
% 219 words
First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
and recursively searched each folder to enumerate C language source code.
From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
Some example data pairs are shown in figure~\ref{fig:pairsoffragments}. 
\\*

\begin{figure}
	\begin{tabular}{|l|l|} \hline
	 C source code & x64 assembly \\ \hline 
		\begin{lstlisting}[style=Csample]
		r *= a;
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
		\end{lstlisting} \\ \hline	
		\begin{lstlisting}[style=Csample]
	while(p >= 0){
		p--;
		r *= a;
	}
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	jmp LABEL_0
LABEL_1 :
	sub DWORD [rbp-0x18],0x1
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
LABEL_0 :
	cmp DWORD [rbp-0x18],0x0
	jns LABEL_1
		\end{lstlisting} \\ \hline		
		\begin{lstlisting}[style=Csample]
int pow(int a,int p){
	int r = 1;
	while(p >= 0){
		p--;
		r *= a;
	}
	return r;
}
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	push rbp
	mov rbp,rsp
	mov DWORD [rbp-0x14],edi
	mov DWORD [rbp-0x18],esi
	mov DWORD [rbp-0x4],0x1
	jmp LABEL_0
LABEL_1 :
	sub DWORD [rbp-0x18],0x1
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
LABEL_0 :
	cmp DWORD [rbp-0x18],0x0
	jns LABEL_1
	mov eax,DWORD [rbp-0x4]
	pop rbp
	ret
		\end{lstlisting} \\ \hline
	\end{tabular}
	\caption{Example of training data pairs}
	\label{fig:pairsoffragments}
\end{figure}

@@

\subsection{Assembly Code Preprocess}
% 155 words
The assemblies were preprocessed in two ways.
First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
So the one byte integer sequences can be directly used for input sequences.
Second way is the tokenized sequence of assembly codes. 
The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated the sequences to one sequence, then we modified followings.
\begin{itemize}
\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
\item 
The relative access of code address, such as {\sl call} or {\sl jump} operations, 
are relabeled like $\alpha$-conversion for making code position independent and for reducing the vocabulary size.
\item The big integer values are substituted. 
In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integeres are substituted with the {\sl \_\_HEX\_\_} symbol.
This also reduces the vocabulary size.
\end{itemize}

@@

\begin{itemize}
\item The variable-ary nodes and optional nodes are converted. 
For example, the {\sl CompoundStatement} node has variable number of statements. 
We converted such list of nodes to the chains of concatnation and terminal, like a list representation in functional language.
Another example is the  {\sl If} statement, whose {\sl else} clausure are sometimes missing. 
We converted such optional node to the alternative of some node and Null node, like a optional data structure in functional language.
\item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
\item There are four type of literals in C language. 
The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
The string, float and character literals are converted to {\sl \_\_LITERAL\_\_} simbol.

Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceibable way,
but we couldn't implement this because of its technical difficalty, so this is left to future work.
\end{itemize}

@@

\begin{figure}[h]
	\begin{tabular}{|c||c|c|c|}
		\hline
		  & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline \hline
		 Generate & \multicolumn{2}{|c|}{token sequence} & AST \\ \hline
		 With Attention & no & \multicolumn{2}{|c|}{yes} \\ \hline
		 Encoder & \multicolumn{3}{|c|}{Bidirectional LSTM} \\ \hline
		Number of LSTM Layers & \multicolumn{3}{|c|}{4} \\ \hline
		% Vector Dim & \multicolumn{3}{|c|}{128} \\ \hline
	\end{tabular}
	\caption{The configuration parameters of the models}
	\label{fig:parameterofmodels}
\end{figure}

@@

@@

For evaluating each model, we randomly sampled 100 data pairs from test cases, generated estimated decompilation results for each test cases,
then averaged the edit distance ratios and BLEU scores between results and ground truths.

@@

We can see that Seq2seqAtt shows slightly better results in both edit distance ratios and BLEU scores, 
while there are no significant difference between Seq2seq and Seq2tree in both metrics.
Seq2seqの結果とSeq2seqAttの結果を比較することにより、attention が性能向上に寄与していることがわかります。
逆にSeq2treeにはattentionがあるにもかかわらずSeq2seqと比較して性能向上が見られなかったわけですが、
これはCのソースコードをASTに変換した際に、データサイズが増えたためであると考えられます。

@@

Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences
, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as AST trees.
The length 
According to the figures, the AST size is 2~3 times larger than that of C source codes.

>>>>

\usepackage{listings}
\usepackage{cite}
\usepackage{url}
\usepackage{natbib}
\usepackage[dvipdfmx]{graphicx}
\usepackage{framed}
\usepackage{caption}

@@

\lstdefinestyle{Csample}{
  language=C,
  tabsize=2,
 	framesep=5pt,
}

\lstdefinestyle{Asmsample}{
  tabsize=2,
  framesep=5pt,
  %frame=none,
}

\lstdefinestyle{ForDecomp}{
  tabsize=2,
  frame=l,
  framesep=5pt
}

\lstset{%
  basicstyle={\small},%
  commentstyle={\small\itshape},%
  keywordstyle={\small\bfseries},%
  % style={myCustomMatlabStyle},
  stringstyle={\small\ttfamily},
  breaklines=true,
  columns=[l]{fullflexible},%
  % frame={tb},
  % numbers=left,%
  xrightmargin=0zw,%
  xleftmargin=3zw,%
  numberstyle={\scriptsize},%
  stepnumber=1,
  numbersep=1zw,%
  lineskip=-0.5ex,%
  captionpos=b,
}

\begin{document}
\begin{eabstract}
A decompiler is a tool for recovering a source code from compiled binary data.
There are various decompilers, but they often output a source code that is not intelligible to humans. 
In this thesis, we apply machine translation techniques to generate human intelligible decompiled source codes. 
More specifically, we propose to use recurrent neural networks with attention, 
which have been demonstrated to be useful for machine translation. 
In experiments, we use source codes collected from open source projects and their binary data for training and evaluating the neural networks.
From the experiment, we can observe little improvement in the decompilation result with the use of attention.
However, the results were not applicable for practical use.

\end{eabstract}
\begin{jabstract}
逆コンパイラはコンパイル後のバイナリデータからソースコードを復元するためのツールである。
様々な逆コンパイラが存在するが、既存の逆コンパイラはしばしば人間にとって分かりにくいソースコードを出力する。
そこで本論文では、統計的機械翻訳の技術を逆コンパイラに用いた、解析者にとってわかりやすいソースコードを出力する逆コンパイラを提案する。
具体的には、機械翻訳において有用とされる注意機構付き再帰型ニューラルネットワークを用いる。
実験では、オープンソースプロジェクトから収集したソースコードとそのバイナリデータを用いてニューラルネットワークを学習し、その性能を検証した。
実験の結果、注意機構を用いることににより逆コンパイル結果における若干の精度向上が認められたが、実用的な精度までは至らなかった。
\end{jabstract}

@@

These days, the amount of malware has been increasing rapidly. In the report of AV-TEST Institute,
over 100 million malwares are newly found in every year for the past five years \citep{malware_increase}.
There are many case studies for malwareinfection \citep{malware_case_1,malware_case_2,malware_case_3,malware_case_4}.
In those cases, they analyse malwares to assess the impact of the incident and to identify the vulnerability which causes the infection.
% Therefore, the importance of developing malware analysis tools has been rising.
% 要参考文献 -> つけた。
In order to analyse malwares quickly and efficiently, there are some tools for analysing malwares \citep{mal_anal_tool}.
One of these tools is a decompiler, which is a tool for analyzing the behavior of malware. 
This tool generates a C-like pseudocode which represents the behavior of the malware, and analysts can infer the behavior of the malware from the pseudocode.
This is much easier compared to analyzing raw binary codes.

@@

In this thesis, we apply neural networks to the problem of decompilation to generate human-friendly pseudocodes. 
This idea is originated from \cite{Motoneta}, in which they used recurrent neural networks, in particular sequence-to-sequence model, for decompilation.
However, their model does not seem to have some features for improving the quality of decompilation.
Therefore, we implemented the attention mechanisme, which is introduced in \cite{dot_attention}, for improving the quality.
Additionaly, the sequence-to-sequence model, which they used for modeling, ignores the structure of the C language code.
Therefore, we also implemented the sequence-to-tree model, which is suggested in \cite{Seq2Tree}, for generating structured C language source code.

In the experiment, we tested three models, the basic sequence-to-sequence model, the sequence-to-sequence model with attention and the sequence-to-tree model.
As the result of the experiment, the attention mechanism showed little improvemtn in the performance, while the sequence-to-tree does not.
Unfortunately, the results were not applicable for practical use, because the most of decompilation results were incorrect.

% In the following part of the paper, we explain the

\chapter{Related Works}
In this section, we review related works.

\section{Decompilation with Machine Learning}

Because perfect decompilation is naturally impossible, there are some machine learning applications for decompilation.

In \cite{Motoneta}, they used the seqence-to-sequence model, which is a popular technique in the machine translation.
The seqence-to-sequence model is also evaluated in this thesis.

@@

@@

\section{Improvement of decompilation results}
In this thesis, we do not try to recover the function name and variable name. 
However, for hand-decompilation, sometimes the name can be estimated by the functionality of the variable.
For example, \cite{hand_decompilation} used Boomerang decompiler and repeatedly fixed variable types and names of the decompilation results 
to recover the source code of a software.

Here, we show a example of the name estimation.
Assume there is a variable X which seems to have a C struct type and has two fields P and Q.
Also, there are two functions F and G which operate with X. 
The function F receives X and another value V, assigns V to the memory indicated by P, adds 8 to P and increases Q. 
The function G receives X, subtracts 8 from P, decreases Q, and returns the value indicated by P.
In the situation, is is estimated that X has a name related to {\sl stuck}, the function F has a name related to {\sl push},
ands G has a name related to {\sl pop}.

@@

\cite{JSNaughty} applied statistical machine translation for this task. 
They calculated the future value of a variable from its functionality, then 
sought the most suitable name from the candidates generated from the corpus.

% 変数の性質から統計情報を取り出し、それを元に

\section{Neural Network for Program Generation}

@@

A compiler is a program which compiles a source code written in language X to another language Y. 
% 文献 Usually, X is a high-level language and Y is relatively a low-level language. 
For example, a Clang compiler translates the C language to the x64 assembly language, a javac compiler translates Java to a Java virtual machine code.
This process is usually

A decompiler is a program which aims to reverse the process of a compiler, retrieving a source code of the high-level language X from a source code of a low-level language Y. 
% 文献
Especially, 
This reverse process is usually insufficient or impossible.
This is because a lot of informaition, such as variable names or function names, are lost when compiling.
Additionally, the program structure described in the high level-language is lost too. 
For example, a simple \texttt{for} statement can be represented by the combination of a \texttt{while} statement and an \texttt{if} statement, or the combination of \texttt{if} statement and \texttt{goto} statement. 
So a decompiler cannot distinguish the difference in their representations, 
although in the real situation \texttt{for} statement are often used and \texttt{goto} statement are rarely used.

% これについてちゃんと書く。
% Their output psudecodes are sometimes wrong or hard to understand.

@@

% \let\oldlstinputlisting\lstinputlisting
% \renewcommand{\lstinputlisting}[2][]{\oldlstinputlisting[frame=lines,#1]{#2}}

\begin{figure}
	\begin{tabular}{cc}
		\begin{minipage}[c]{0.5\hsize}
		\begin{framed}
			\lstinputlisting[breaklines=false]{insert_list.c}
			\end{framed}
			\caption*{Sample C source code}
		\end{minipage}
		\\
		\begin{minipage}[c]{0.5\hsize} %title={Result of the Hopper Decompiler}
			\begin{framed}
			\lstinputlisting[]{snowman.c}
			\end{framed}
			\caption*{Result of the Snowman Decompiler}
		\end{minipage}
		\begin{minipage}[c]{0.5\hsize}
			\begin{framed}
			\lstinputlisting[]{recstudio.c}
			\end{framed}
			\caption*{Result of the REC Studio Decompiler}
		\end{minipage}
	\end{tabular}
	\vspace*{-0.6cm}
	\caption{Decompilation results of existing decompilers for C source code}
	\label{fig:cw}
\end{figure}

Figure~\ref{fig:cw} shows an example of decompilation results of the Snowman decompiler version v0.1.3 and the REC Studio decompiler version 4.1 
for a sample C language code. The sample C code is compiled by the GNU C Compiler version 4.8.5, with the optimization level \texttt{-O0}.
The REC decompiler missed the structure of the variable \texttt{root}.
It also failed to estimate the number of arguments and the return value of the function.
The Snowman Decompiler succeeded to reconstruct the structure of the variable as \texttt{struct s0}.
It also succeeded to estimate the number of arguments and the return value as the semantically correct expressions, 
however the statement \texttt{return 0;} is reconstructed to the complex combination of statements.

These incorrect or verbose results might be due to missing patterns in the assembly codes. 
Existing decompilers are made up with many steps similarly to compilers \citep{decompiler_path,hex_rays}.
In each step, a decompiler finds patterns in binary data, converts them to more high-level structure.
However, covering all patterns might be hardly impossible, since there are many compilers and compiler optimizations.
文献欲しいが見当たらない...

Therefore, applying statical machine

% These patterns comprehensive

% The pathes are made up of

% The \texttt{for} statement in the C source code is 
% reconstructed to the combination of the \texttt{while} statement and the {\sl if} statement in both decompiler results.

% This is the example of the impossibleness of the perfect decompilation, what we mentioned.

% However, there are many patterns

% Existing decompilers are made up with many steps similarly to compilers. \citep{hex_rays,}
% They find patterns in binary data, convert them to more high-level structure, and chain them so that they can finally generate a high-level psudecode.

% このへん嘘書いてたので修正。
% The Hopper decompiler fails to detect while statements, and the variable {\sl now} is incorrectly analyzed.
% The output of snowman seems rather correct, as type {\sl struct tree} is reconstructed to {\sl struct s0}, 
% and the {\sl if} statement and {\sl while} statement are correctly restored. 
% However, it fails to detect the function epilogue, and the {\sl free} function call is incorrectly analyzed.
% Ideally, the decompilers can find correct function ranges and structure of statements, but they failed.

@@

% 189
In this thesis, we try to apply statistical approach, specifically SMT (statistical machine translation) technique, for decompilation.
The decompilation problem is formulated as follows.

@@

\subsection{Sequence-to-Sequence}
% This model is called seq2seq (sequence to seqence) model.

@@

% ビームサーチ書く。
% For TODO

@@

Second is the multi-layer reccurent neural networks, introduced in \cite{multi_layer}.
They reported that, feeding the output sequence of the LSTM network to another LSTM network, like stucking the network layers, will improve the accuracy of the prediction.
This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.

@@

\subsection{Sequence-to-Tree}
% 184 words
Compare to natural languages, programming languages obeys rigid grammers. % wich are usually context free grammers.
Therefore, it is reasonable to consider the grammer of the programming language when generating programs.
Sequence-to-Tree is a model for generating tree-structured output from sequence input. 
This model is introduced in \cite{Seq2Tree} for generating a program from a program specification written in the natural language. 
This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.

@@

\begin{figure}[]
	\begin{center}
	\includegraphics[height=12cm]{ast_zu.png}
	\end{center}
	\caption{AST representation of a C statement \texttt{b = a + 3;} }
	\label{fig:ast_zu}
\end{figure}

The decoder network is a network for generating tree structured output. 
A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
For example, the tree shown in figre~\ref{fig:ast_zu} is gererated from the sequence $ [act_1, \dots act_{12}] $, 
where action $ act_k $ expands the left-most nonterminal symbol in the tree generated from the action sequence $ [act_1, \dots act_{k-1}] $. 
Suppose the tree $ty$ is generated by the action sequence $ [act_1, \dots act_m] $, 
then the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(act_k|sx,[act_1, \dots act_{k-1}]) $. 
The sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
calculating $ LSTM_{dec}(dec_{k},av_{k}) $ sequentially for estimating $p(act_{k+1}|sx,[act_1, \dots act_{k}]) $.

@@

They also used devised method for generating terminal symbols, because they need to copy the name of some variables from the program specification.
However, in our case, we do not need copy the information from the input, because the name information is lost when compiling.
Nevertheless, it is found from the experiments that our decompilers often fail to recover the constant values in the programs.
Therefore, implementing the copying method is left for future work.

@@

\section{Data Collection}
% 219 words
First, we collected source codes by crawling \cite[GitHub]{github}, cloning about 900 repositories with C language topic, 
and recursively searched each folder to enumerate C language source code.
From each source code, we generated pairs of C source code fragment and x64 assembly code corresponds to the C fragment.
Some example data pairs are shown in figure~\ref{fig:pairsoffragments}.

\begin{figure}
	\begin{tabular}{|l|l|} \hline
	 C source code & x64 assembly \\ \hline 
		\begin{lstlisting}[style=Csample]
		r *= a
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
		\end{lstlisting} \\ \hline	
		\begin{lstlisting}[style=Csample]
	while(p >= 0){
		p--;
		r *= a;
	}
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	jmp LABEL_0
LABEL_1 :
	sub DWORD [rbp-0x18],0x1
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
LABEL_0 :
	cmp DWORD [rbp-0x18],0x0
	jns LABEL_1
		\end{lstlisting} \\ \hline		
		\begin{lstlisting}[style=Csample]
int pow(int a,int p){
	int r = 1;
	while(p >= 0){
		p--;
		r *= a;
	}
	return r;
}
		\end{lstlisting}
		&
		\begin{lstlisting}[style=Asmsample]
	push rbp
	mov rbp,rsp
	mov DWORD [rbp-0x14],edi
	mov DWORD [rbp-0x18],esi
	mov DWORD [rbp-0x4],0x1
	jmp LABEL_0
LABEL_1 :
	sub DWORD [rbp-0x18],0x1
	mov eax,DWORD [rbp-0x4]
	imul eax,DWORD [rbp-0x14]
	mov DWORD [rbp-0x4],eax
LABEL_0 :
	cmp DWORD [rbp-0x18],0x0
	jns LABEL_1
	mov eax,DWORD [rbp-0x4]
	pop rbp
	ret
		\end{lstlisting} \\ \hline
	\end{tabular}
	\caption{Example of training data pairs}
	\label{fig:pairsoffragments}
\end{figure}

@@

\subsection{Assembly Code Preprocess}
% 155 words
There are two ways for preprocessing assembly codes.

First way is the raw binary integers. The assemblies are finally assembled to the sequence of the one byte integers, ranged from 0 to 255.
So the one byte integer sequences can be directly used for input sequences.

Second way is the tokenized sequence of assembly codes. 
The disassembled opcodes and operands in {\sl S5} are split to symbols, and concatenated these sequences to one sequence, then we modified followings.
\begin{itemize}
\item For each end of the operations, the {\sl ENDLINE} symbol is added to indicate the end of operation.
\item 
The relative access of code address, such as {\sl call} or {\sl jump} operations, 
are relabeled like $\alpha$-conversion for making code position independent and for reducing the vocabulary size.
\item The big integer values are substituted. 
In detail, the integer in the range from -255 to 256 are preserved as it is, and the other integeres are substituted with the {\sl \_\_HEX\_\_} symbol.
This also reduces the vocabulary size.
\end{itemize}

We choiced second way for the experiment.
This is because, in our case, the assembly code is generated from common C compiler, therefore the assembly code can be disassembled uniquely.
For example, \cite{disasm_obfuscate} proposed a obfuscation technique, which deceives the disassembler to generate wrong disassembly result.
In that case, the first way might be better than the second way.

@@

\begin{itemize}
\item The variable-ary nodes and optional nodes are converted. 
For example, the {\sl CompoundStatement} node has variable number of statements. 
We converted such list of nodes to the chains of concatnation {\sl CONS} and termination {\sl NIL}, like a list representation in functional language.
Another example is the  {\sl If} statement, whose {\sl else} clausure are sometimes missing. 
We converted such optional node to the alternative of {\sl SOME} and {\sl NONE}, like a optional data structure in functional language.
\item The variable names, function names, label names, or type names were renamed like $\alpha$-conversion.
\item There are four type of literals in C language. 
The integer literal less than 256 is preserved, and the literal greater than 256 is clipped to 256.
The string, float and character literals are converted to {\sl \_\_LITERAL\_\_} simbol.

Modifying the node to indicate the value in the assembly code corresponding to the literal is also conceibable way,
but we did not implement this because of its technical difficalty, so this is left to future work.
\end{itemize}

@@

\begin{figure}[h]
	\begin{tabular}{|c||c|c|c|}
		\hline
		  & Seq2seq & Seq2seqAtt & Seq2tree \\ \hline \hline
		 Generate & \multicolumn{2}{|c|}{token sequence} & AST \\ \hline
		 With Attention & no & \multicolumn{2}{|c|}{yes} \\ \hline
		 Encoder & \multicolumn{3}{|c|}{Bidirectional LSTM} \\ \hline
		Number of LSTM Layers & \multicolumn{3}{|c|}{4} \\ \hline
		Dimensionality of Vector Embedding & \multicolumn{3}{|c|}{128} \\ \hline
	\end{tabular}
	\caption{The configuration parameters of the models}
	\label{fig:parameterofmodels}
\end{figure}

@@

% \section{Furure work}

@@

\section{Numerical Evaluation}
For evaluating each model, we randomly sampled 100 data pairs from test cases, generated estimated decompilation results for each test cases,
then averaged the edit distance ratios and BLEU scores between results and ground truths.

@@

We can see that Seq2seqAtt shows slightly better results in both edit distance ratios and BLEU scores,
 which implies that the attention improves the performance of the decompilation.
However, there are no significant difference between Seq2seq and Seq2tree in both metrics.
This seems to be due to the length of the sequences to be estimated.
% Seq2seqの結果とSeq2seqAttの結果を比較することにより、attention が性能向上に寄与していることがわかります。
% 逆にSeq2treeにはattentionがあるにもかかわらずSeq2seqと比較して性能向上が見られなかったわけですが、
% これはCのソースコードをASTに変換した際に、データサイズが増えたためであると考えられます。

@@

Figure~\ref{fig:csizes} shows the length distribution of the dataset as C token sequences
, and figure~\ref{fig:astsizes} shows the size distribution of the same dataset as ASTs.
The size of a AST is equals to the length of its action sequence.
According to the two figures, the AST size is 2~3 times larger than the length of C token sequences.
Therefore, the AST estimation may be harder than C token sequence estimation.

\begin{figure}
	\begin{tabular}{|l|l|} \hline
	 ground truth & 
		\begin{lstlisting}[style=Csample]
r *= a
		\end{lstlisting} \\ \hline
		Seq2Seq & 
		\begin{lstlisting}[style=Csample]
const unsigned int V0 = V1 * floatliteral
		\end{lstlisting} \\ \hline
		Seq2SeqAtt & 
		\begin{lstlisting}[style=Csample]
V0 = ( unsigned int ) ( V1 ) * ( unsigned int ) V2
		\end{lstlisting} \\ \hline
		Seq2Tree & 
		\begin{lstlisting}[style=Csample]
V0 = V0 * V1
		\end{lstlisting} \\ \hline
		\hline	
	 ground truth & 
		\begin{lstlisting}[style=Csample]
while(p >= 0){
	p--;
	r *= a;
}
		\end{lstlisting} \\ \hline
		Seq2Seq & 
		\begin{lstlisting}[style=Csample]
for(;V0 = (1<<(((unsigned int)-1<<((32-20)-1))-1))
*((unsigned char*)(V1.V2))[1] = (unsigned char)2;
}
		\end{lstlisting} \\ \hline
		Seq2SeqAtt & 
		\begin{lstlisting}[style=Csample]
while(((void *) >= 0) != ((void *) 0)){ 
	return ((void *) 0);
} else { 
	V0 = (( void * ) 0); 
}
		\end{lstlisting} \\ \hline
		Seq2Tree & 
		\begin{lstlisting}[style=Csample]
while(V0 < 0){ 
	V1 = V0 - 1;
}
		\end{lstlisting}
		 \\ \hline	\hline
	 ground truth & 
		\begin{lstlisting}[style=Csample]
int pow(int a,int p){
	int r = 1;
	while(p >= 0){
		p--;
		r *= a;
	}
	return r;
}
		\end{lstlisting} \\ \hline
		Seq2Seq & 
		\begin{lstlisting}[style=Csample]
void V0(int V1,int V1){ 
	int V1 = 0; 
	int V1; 
	for(V2=1;V1<=V2;++V2){ 
		V1 = * V3; 
	} 
}
		\end{lstlisting} \\ \hline
		Seq2SeqAtt & 
		\begin{lstlisting}[style=Csample]
void V0(unsigned int V1,unsigned int V2){ 
	unsigned int V1 = ((void *) 0); 
	unsigned int V3 = ((void *) 0); 
	unsigned int V1 = ((((void *) 0) != ((void *) 0))); 
	return V4; 
}
	\end{lstlisting} \\ \hline
		Seq2Tree & 
		\begin{lstlisting}[style=Csample]
INVALID_FUNCTION_DECL { 
	TRANCATETRANCATE 
}
		\end{lstlisting}
		 \\ \hline	
	\end{tabular}
	\caption{Smaple translation results for each model}
	\label{fig:sampletranse}
\end{figure}

\section{Sampled Decompilation Results}

Figure~\ref{fig:sampletranse} shows sample translate results for each model.

For the first short example, each of the models recovered that the C statement is composed of multiplication and assignment,
while only Seq2Tree recovered the name of the variables, and Seq2Seq and Seq2SeqAtt were failed to recover.
